My title

### 2024-12-02 paper/paper.qmd
updated preable first version of abstract updated required libraries

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Dennis Netchitailo
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Dennis Netchitailo
thanks: "Code and data are available at: 
[https://github.com/dennisnetchitailo/STA304P3]
(https://github.com/tacookson/data/tree/master/britain-bombing-ww2)."
date: 2 December 2024
date-format: long
abstract: "This study models the German bombing campaign of Britain during the Second World War by analyzing the data collected by the Home Security War Room from 1939 to 1945 to summarise air raid damage. I use a multiple linear regression model to estimate the impact of the time an attack occurred on casualties."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(here)

```
